---
title: "GroupWork727_Masters"
author: "Fred LaPolla"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RCurl)
url <- getURL("https://raw.githubusercontent.com/fredwillie/RScience2020/master/NYC_HANES_DIAB.csv")
nyc <- read.csv(text = url)
nyc$DX_DBTS <- factor(nyc$DX_DBTS, levels = 1:3, labels = c("Diabetes w/ DX", "Diabetes no DX", "No Diabetes"))
```


## Group Work

Try out using GGplot to make a scatter plot of A1C vs Glucose. Remember there will be two parts: where you assign the aes and then where you add a geom

```{r}

```

## Group work

Try making the same A1C vs Glucose scatter plot but add in a line estimating linear correlation:

```{r}

```

## Group work

Make a histogram of lead levels, experiment with updating the binwidth. Make a boxplot of diabetes diagnosis vs glucos level.

```{r}

```


## Group Work

Try making a bar chart with error bars for mean Glucose by diabetes diagnosis

```{r}

```

## Group Work

Explore the palettes on R color brewer. Try changing the color scale on a scatter plot of glucose vs. A1C

```{r}

```


## Group work

Try adjusting the X and Y scales to be in increments of 50 for glucose, 2 for A1C in your scatter plot of A1C vs Glucose. Change the theme (background), update the X and Y labels to say "A1C level" and "Glucose level".

```{r}

```