---
title: "Masters Homework 3"
author: "Fred LaPolla"
date: "6/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


>- Subset to only have females (gender == "Female")

```{r}

```


>- Create a subset of males and find the median total cholesterol level

```{r}

```


>- Try to create a summary of the mean A1C using two factors, GENDER and DX_DBTS

```{r}

```

Find the class of the first three columns of data. What are they?

```{r}

```

How does R treat blank values?

What command can be used to identify where NAs are located in a column?

```{r}

```


How can you use indexing to create a subset without any NAs?

```{r}

```

How could you delete a column of data, for example, the 5th 
```{r}

```


What command would let you find a set of text in the cells of a column?

```{r}

```


Rename the HSQ1 variable to Health_Status

```{r}

```

Explore the Mutate command and create a ratio of total cholesterol divided by HDL

```{r}

```



>- Why would one use a visualization for exploratory analysis?

>- What information about the nature of our data can a histogram tell us?

>- Make a histogram on your own on one column from the nyc data frame. Is it skewed? Which way? Try confirming with pastecs::stat.desc (hint set norm = TRUE as an argument).

```{r}

```

>- Try making a QQPlot to assess the normality of one variable of your choosing. Is the distribution normal? How can you tell?

```{r}

```

>- Make a boxplot glucose levels by diabetes diagnosis:

```{r}


```

